Exposing and Exploring Disputed Statements on the Web

### 2009-03-31 papers/uist_thinklink/thinklink.tex
Paper changes from Tye. Fixed UI glitches revealed when running on windows

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=5cm]{../screenshots/highlight_crop.png}
	\caption{Think Link highlights snippets that make disputed claims}
	\label{highlight}
	\end{center}
\end{figure}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/v2_popup_dim.png}
	\caption{Click on a snippet to investigate evidence for the claim it makes}
	\label{claimview}
	\end{center}
\end{figure}

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners investigated to determine whether they are true. 
Think Link's database automatically imports all contentious claims identified by Snopes.
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. 
%We use Fact Check as a useful source of disputed claims.

@@

NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias. NewsCube finds articles on the same topic that have different biases. MediaCloud shows which different words different news sources associate with the same topic.

Several authors have created tools that help users know when to trust information on Wikipedia\footnote{http://wikipedia.org}. WikiTrust~\cite{Adler2008a} highlights passages on wikipedia that have been written recently or written by untrusted editors. Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest.

@@

Tagging Systems~\cite{Marlow2006,Golder2006} allow users to collect and organize information by associating it with an ad-hoc collection of tags. Notable tagging systems include del.icio.us\footnote{http://del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos.

@@

Videolyzer~\cite{Diakopoulos2008}\footnote{http:\\www.videolyzer.com} allows users to annotate and comment on political videos. A user can attach a comment to a section of video and tag it for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made. Like SpinSpotter, Videolyzer does not attempt to gather multiple video sections that make a common contentious claim.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books.

@@

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8.5cm]{../screenshots/v2_panels.png}
	\caption{The claim graph consists of a series of linked panels}
	\label{panels}
	\end{center}
\end{figure}

@@

In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of an expanding horizontal array of panels where each panel provides information about the item that is selected in the panel to its left. If a user clicks on a link in a panel then a new panel opens to the right giving more information about the linked node. To emphasize the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

The panel for a claim (Figure~\ref{panel}) lists evidence that will help inform the users opinion about the claim and alternative points of view. Evidence is categorized as either supporting, opposing, or being related-to the claim. The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument. Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.  The panel for a snippet shows the snippet text in the context of the web page it is part of. This, combined with the cascading panel interface allows a user to quickly read the evidence for and against a claim without having to leave the claim browser interface.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/v2_panel.png}
	\caption{A claim panel presents information for and against a claim}
	\label{panel}
	\end{center}
\end{figure}

@@

Think Link's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to relation. 
While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link is designed for. 
We have also found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.

@@

One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions. Think Link uses several strategies to try to avoid this happening. Firstly, positive votes count for more than negative votes. Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent. Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side. In some cases, it may still be necessary to introduce a moderation system similar to that used in Wikipedia, where trusted users can override popular opinion when things go wrong. 
\todo{Talk about whether we know if this works}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/v2_sniptopic.png}
	\caption{Snippet first: Pick a claim or topic for each unfiled snippet}
	\label{sniptopic}
	\end{center}
\end{figure}

@@

Participants were shown the prototype interface shown in Figures~\ref{secondbrowser} and \ref{secondsnippetbox}. This was similar to the interface described earlier in this paper, except that it used drag and drop to make connections rather than a suggestion system, it did not offer a ``relates-to'' link between claims, and it required a user to choose a claim at the point at which they create a snippet.

@@

Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader). One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''. A smaller number said they would want to mark up claims they disagreed with (activist). One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.

@@

Several users got confused by claims that referred to similar events at different points in time. 
For example, one participant in the first study marked a two claims as opposing each other when each was true at the time that it was written. This is a particular problem when talking about breaking news events, where the facts can change fast. If Think Link is to be effective for describing such events then it will need to have better support associating times with claims and snippets.

Several users expressed an interest in being able to mark a claim as disputed without having to find opposing evidence. One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence. In the future we are planning to implement a social voting system to allow users to say what claims they believe are false and see what claims their friends agreed or disagreed with.

\begin{figure}[tb]
	\includegraphics[width=8.5cm]{../screenshots/oldpoint_diagram.png}
	\caption{First Prototype Claim Browser}
	\label{oldbrowser}
\end{figure}

\begin{figure}[tb]
\begin{center}
	\includegraphics[width=5cm]{../screenshots/claimbrowse.png}
	\caption{Second Prototype Claim Browser}
	\label{secondbrowser}
\end{center}
\end{figure}

@@

Acknowledgements omitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http:\\famfamfam.com} collection.

>>>>

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/v2_highlight_shadow.png}
	\caption{Think Link highlights snippets that make disputed claims}
	\label{highlight}
	\end{center}
\end{figure}

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/v2_popup_dim2.png}
	\caption{Click on a snippet to investigate evidence for the claim it makes}
	\label{claimview}
	\end{center}
\end{figure}

@@

@@

If one sees a claim on the web that one suspects might be untrue then one can look it up on Snopes\footnote{http://snopes.com} or FactCheck\footnote{http://factcheck.org}. Snopes is a database of urban legends that the site owners investigated to determine whether they are true. 
Think Link's database automatically imports all contentious claims identified by Snopes.
FactCheck is a web site that investigates claims being made by US political parties and attempts to uncover the facts. The advantage of Think Link is that it tells you when information on web sites is disputed automatically, without requiring you to suspect that information might be disputed and look for it on another site.

%We use Fact Check as a useful source of disputed claims.

@@

NewsCube~\cite{Park2009} and MediaCloud\footnote{http://mediacloud.org} use statistics to help readers avoid media bias. NewsCube finds articles on the same topic that have different biases. MediaCloud shows which different words different news sources associate with the same topic. Unlike Think Link, these tools find contrasting pages about broad topics, rather than trying to find particular claims that are disputed or snippets that make disputed claims.

Several authors have created tools that help users know when to trust information on Wikipedia\footnote{http://wikipedia.org}. WikiTrust~\cite{Adler2008a} highlights passages on wikipedia that have been written recently or written by untrusted editors. Wiki Dashboard~\cite{Kittur2008} creates a visualization of the edit history of a Wikipedia article that lets a user see how contentious it is. Wiki Scanner\footnote{http://wikiscanner.virgil.gr} finds cases where a Wikipedia edit has been made by someone with a conflict of interest. Unlike these Wikipedia-based systems, Think Link does not use edit history to determine when text is untrustworthy; rather it relies on a community of activist users.

@@

Tagging Systems~\cite{Marlow2006,Golder2006} allow users to collect and organize information by associating it with an ad-hoc collection of tags. Notable tagging systems include del.icio.us\footnote{http://del.icio.us} which uses tags to organize web pages, and Flickr\footnote{http://flickr.com} which associates tags with photos. While Think Link also allows users to organize information from other sources, it does not use tags.

@@

Videolyzer~\cite{Diakopoulos2008}\footnote{http://www.videolyzer.com} allows users to annotate and comment on political videos. A user can attach a comment to a section of video and tag it for bias, accuracy, or rhetorical technique. Comments can include references to external sources that back up the argument being made. Like SpinSpotter, Videolyzer does not attempt to gather multiple video sections that make a common contentious claim.

@@

Several tools layer an alternative navigation graph over information on the web. TextRunner~\cite{Etzioni2008} and Idea Navigation~\cite{Etzioni2008} look for instances of subject-verb-object triples on web pages and connect these together as a graph in which objects are linked by statements made about them on different web pages. ScentHighlights~\cite{Chi2005a} highlights snippets of text that relate to topics the user has expressed interest in. Kolak and Schillit~\cite{Kolak2008} detect cases where one book has quoted from another one, and use this to create links between books. Think Link also creates new links between information, but it's links are created by users, rather than being mined automatically.

@@

\begin{figure*}[tb]
	\begin{center}
	\includegraphics[width=18cm]{../screenshots/v2_panels2.png}
	\caption{The claim graph consists of an expanding sequence of linked panels}
	\label{panels}
	\end{center}
\end{figure*}

@@

@@

In our user studies, we found that sceptical readers wanted to be able to investigate the evidence for and against a claim without having to navigate away from that claim. We thus created an interface that consists of an expanding horizontal array of panels where each panel provides information about the item that is selected in the panel to its left (Figure~\ref{panels}). If a user clicks on a link in a panel then a new panel opens to the right giving more information about the linked node. To emphasize the connection between the panels, the claim browser places an arrow next to each selected item, pointing to the panel that gives more information about that item.

The panel for a claim (third panel in Figure~\ref{panels}) lists evidence that will help inform the users opinion about the claim and alternative points of view. Evidence is categorized as either supporting, opposing, or being related-to the claim. The ``related-to'' category is used for evidence that does not fit neatly into one side of the argument. Evidence can either be a snippet that talks about that claim, or another claim whose truth would support or oppose this claim.  The panel for a snippet (last panel in Figure~\ref{panels}) shows the snippet text in the context of the web page it is part of. This, combined with the cascading panel interface allows a user to quickly read the evidence for and against a claim without having to leave the claim browser interface.

@@

% \begin{figure}[tb]
% 	\begin{center}
% 	\includegraphics[width=6cm]{../screenshots/v2_panel.png}
% 	\caption{A claim panel presents information for and against a claim}
% 	\label{panel}
% 	\end{center}
% \end{figure}

@@

Think Link's graph model is simpler than that used by gIBIS~\cite{Conklin1987a}: we don't distinguish between an argument and a position, we allow a claim to relate-to another claim without supporting or opposing it, we merge issues with topics, and we collapse gIBIS's five ways of connecting issues together and four ways of connecting a claim to an issue into a single relates-to link type. 
While Think Link's simplified graph structure is arguably less useful for the argument modelling and resolution task that gIBIS was designed for, we have found that it is sufficient for the conflict discovery and snippet organization task that Think Link is designed for. 
We have also found that the smaller set of less precise link and node types reduces the mental effort required to create an argument graph.

@@

One danger in a voting system is that a large group of people may drown out the opinions of their opponents by voting down their opinions. Think Link uses two strategies to try to reduce this problem. Firstly, positive votes count for more than negative votes. Thus if two different groups are voting up their own evidence and voting down the opposing group's evidence, it is still likely that the opinions of both groups will be relatively prominent. Secondly, a piece of evidence only competes against other pieces of evidence on the same side of the argument, thus even if supporters of one side are voting up their own evidence, this will not push down evidence on the other side -- though of course they may vote up bad arguments for the opposing point of view. We anticipate that we will eventually need to introduce a moderation system similar to that used in Wikipedia, allowing trusted users to override popular opinion when things go wrong. 
\todo{Talk about whether we know if this works}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8.5cm]{../screenshots/v2_sniptopic.png}
	\caption{Snippet first: Pick a claim or topic for each unfiled snippet}
	\label{sniptopic}
	\end{center}
\end{figure}

@@

Participants were shown the prototype interface shown in Figures~\ref{secondbrowser} and \ref{secondsnippetbox}. This was similar to the interface described earlier in this paper, except that it used drag and drop to make connections rather than a suggestion system, it did not offer a ``relates-to'' link between claims, it required a user to choose a claim at the point at which they create a snippet, and the claim browser only showed one panel at a time.

@@

Most participants said that they would want to use Think Link to tell them when information they read was disputed (sceptical reader). One participant said ``The web needs to be taken with a grain of salt, and this gives you salt goggles''. A smaller number said they would be likely to mark up claims they disagreed with (activist). One participant who was a political blogger was very excited about the ability to mark up things he thought were lies.

@@

Several users got confused by claims that referred to similar events at different points in time. 
For example, one participant in the first study marked two claims as opposing each other when each was true at the time that it was written. This is a particular problem when talking about breaking news events, where the facts can change fast. If Think Link is to be effective for describing such events then it will need to have better support associating times with claims and snippets.

Several users expressed an interest in being able to mark a claim as disputed without having to find opposing evidence. One user said that opposing a claim required ``too many clicks'' and they wanted to be able to just vote against a claim without having to say why or find evidence. In the future we are planning to allow users to say what claims they personally believe are true or false and see what claims their friends agreed or disagreed with.

\begin{figure}[tb]
	\includegraphics[width=8cm]{../screenshots/oldpoint_diagram.png}
	\caption{First Prototype Claim Browser}
	\label{oldbrowser}
\end{figure}

\begin{figure}[tb]
\begin{center}
	\includegraphics[width=5.5cm]{../screenshots/claimbrowse.png}
	\caption{Second Prototype Claim Browser}
	\label{secondbrowser}
\end{center}
\end{figure}

@@

Acknowledgements omitted for blind submission. Think Link uses icons from the free FamFamFam Silk\footnote{http://famfamfam.com} collection.
